The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-07-01 cordillera-climate.tex
Put floats to the end for review
Rework the introduction
Using from Arjen, Qiong and Irina. Hopefully this is close to last version.
Physically moved floats to the end

@@

% Extra packages
\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{framed}

@@

% All floats at the end of the manuscripts
%\usepackage{endfloat}

@@

% ----------------------------------------------------------------------
\begin{document}

\title{The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the last glacial maximum}
\runningtitle{Climate forcing for Cordilleran ice sheet simulations}

%\author{Julien Seguinot et al.}
%\affil{Department of Physical Geography and Quaternary Geology, Stockholm University, S-106 91 Stockholm, Sweden}
\runningauthor{J. Seguinot et al.}
\correspondence{J. Seguinot\\ (julien.seguinot@natgeo.su.se)}

\received{}
\pubdiscuss{}
\revised{}
\accepted{}
\published{}

\maketitle

% ----------------------------------------------------------------------
\begin{abstract}
\julien[noline]{The abstract is preliminary.}
We present an ensemble of numerical simulations of the former Cordilleran ice sheet forced by present-day climatologies from five different datasets. Surface air temperature and precipitation rates from the NCEP/NCAR reanalysis, the Climate Forecast System Reanalysis, the ERA-Interim reanalysis and the North American Regional Reanalysis are used to force the ice sheet model PISM. Glacial conditions are mimicked by applying constant temperature offsets over the entire modelling domain, and a positive degree-day model is used to compute surface mass balance. The modelled ice sheet appears highly sensitive to the choice of climate forcing. Best results were obtained from the North American Regional Reanalysis, a high-resolution regional reanalysis which assimilates precipitation.
\end{abstract}
% ----------------------------------------------------------------------

% ----------------------------------------------------------------------
\input{sections/intro}
\input{sections/climate}
\input{sections/model}
\input{sections/results}
\input{sections/discuss}
% ----------------------------------------------------------------------

% ----------------------------------------------------------------------
\conclusions  %% \conclusions[modified heading if necessary]
\label{sec:conclusion}
\emph{Coming soon...}
% ----------------------------------------------------------------------

% ----------------------------------------------------------------------
%\begin{acknowledgements}
%\end{acknowledgements}
% ----------------------------------------------------------------------

\bibliographystyle{copernicus}
\bibliography{references}
\end{document}

>>>>

% cordillera-climate.tex
% ----------------------------------------------------------------------

@@

% Coloured hyperlinks
\usepackage[colorlinks,citecolor=blue]{hyperref}

@@

@@

% ----------------------------------------------------------------------
\begin{document}
% ----------------------------------------------------------------------

% Title and authors
\title{The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum}
\runningtitle{Climate forcing for Cordilleran ice sheet simulations}
%\author{Julien Seguinot et al.}
%\affil{Department of Physical Geography and Quaternary Geology, Stockholm University, S-106 91 Stockholm, Sweden}
\runningauthor{J. Seguinot et al.}
\correspondence{J. Seguinot\\ (julien.seguinot@natgeo.su.se)}

% For Copernicus
\received{}
\pubdiscuss{}
\revised{}
\accepted{}
\published{}

% Title
\maketitle

% Sections
\input{sections/abstract}
\input{sections/intro}
\input{sections/climate}
\input{sections/model}
\input{sections/results}
\input{sections/discuss}
\input{sections/concl}

% Acknowledgements
%\begin{acknowledgements}
%\end{acknowledgements}

% References
\bibliographystyle{copernicus}
\bibliography{references}

% Floats
\input{floats/tables}
\input{floats/figures}
\end{document}

### 2013-07-01 floats/figures.tex
Physically moved floats to the end

% ----------------------------------------------------------------------
\section{Results}
\label{sec:results}
% ----------------------------------------------------------------------

Using climate forcing from WorldClim data, the NCEP/NCAR, ERA-Iterim, CFSR and NARR reanalyses described in section~\ref{sec:climate} and the ice sheet model described in section~\ref{sec:model}, we run simulations of glacial inception and growth of the Cordilleran ice sheet using different temperature offsets.

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-cool06}
	\end{center}
	\caption{Ice surface topography (black contours every 1000\,m) and velocity (\unit{m\,yr^{-1}}) after 10\,kyr under a climate 6\degC colder than present for each climate forcing.}
	\label{fig:cool06}
\end{figure*}

Figure~\ref{fig:cool06} shows the outcome of simulations run with a 6\degC temperature offset for each of the 6 climate forcings. In all simulations, ice accumulates and glaciers form as a result of the artificially cooled climate. Yet the magnitude of glaciation appears very different from one climate forcing to another. Whereas the NCAR and CFSR forcings produce a large ice sheet that covers most of the model domain land, the WorldClim, ERA-Interim and NARR forcings lead to more restrictive ice cover, bounded to mountain ice caps in the case of WorldClim data. The smoothing of CFSR precipitation data has limited visual effect on the resulting ice sheet geometry.

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-extent}
	\end{center}
	\caption{Extent of ice cover after 10\,kyr as a function of applied temperature offsets for each climate forcing.}
	\label{fig:extent}
\end{figure*}

As we aim to model an ice sheet approaching LGM size, and consider temperature offset as an unknown parameter in this study, we ran simulations using offset values ranging from 2 to 9\degC for each climate forcing.

Figure~\ref{fig:extent} shows the extent of ice cover at the end of each of these~(48) simulations, grouped by climate forcing. It is again visible that different forcings generally lead to very different final ice cover. Notably, for the smallest temperature offset value of 2\degC that was used, NCAR and CFSR simulations lead to an ice-sheet, whereas WorldClim, NARR and ERA-Interim produced local ice caps only, restricted to the Wrangell-St.~Elias mountains in the case of WorldClim, an area presently glaciated. Several of the NCAR and CFSR simulations produced oversized ice-sheets whose extent is primirily bounded by the model domain boundary conditions rather than physical processes. Differences in regional patterns can also be noted. For instance ERA-Interim ice sheets generally appear more northernly-centered than NARR ice sheets.

\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=9cm]{cordillera-climate-ivolarea}
	\end{center}
	\julien[inline]{I will make the figure readable in black-and-white and highlight markers corresponding to the ``best'' runs.}
	\caption{Total ice volume and glaciated area after 10\,kyr as a function of temperature offset and climate forcing.}
	\label{fig:ivolarea}
\end{figure}

Final ice volume and final ice coverage at the end of all simulations is quantified in Figure~\ref{fig:ivolarea}. The NCEP/NCAR and CFSR forcing lead to a much larger and more extensive glaciation than the ERA-Interim, NARR and WorldClim forcings. The ERA-Interim and NARR lead to similar ice volumes and glaciated areas, yet regional patterns are different, as shown by Figure~\ref{fig:extent}.

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-best}
	\end{center}
	\caption{Ice surface topography (black contours every 1000\,m) after 10\,kyr using temperature offsets that lead to similar areas of ice cover for each climate forcing. 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) ice margin (blue line) from \citet{dyke-2004}.}
	\label{fig:best}
\end{figure*}

To compare modelled ice sheets of similar size, we selected for each climate forcing the simulation that lead to a glaciated area closest to an arbitrary target of $4\,\times10^6\,\unit{km^2}$. These qualitative ``best'' runs are presented in Figure~\ref{fig:best} along the associated temperature offset values. We observe that although similar in size, the selected ice sheets are different in shape and flow patterns. More specifically, NCEP/NCAR, CFSR and ERA-Interim ice sheets cover large territories in Yukon and Alaska that where shown to have remained ice-free for at least several glacial cycles \citep{dukrodkin-1999,kaufman-manley-2004}.

>>>>

% floats/figures.tex
% ----------------------------------------------------------------------

% fig:locmap
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America. The frame delimits this study's modelling domain. The outlines of the former ice sheets depict ice cover at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) after \cite{dyke-2004}. The background map was made with ETOPO1 (\cite{data:etopo1}) and Natural Earth Data (\cite{data:naturalearth}).}
	\label{fig:locmap}
\end{figure}

% fig:temp
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-temp}
	\end{center}
	\caption{Summer temperature maps from the five datasets used in this study and winter temperature map from the WorldClim dataset.}
	\label{fig:temp}
\end{figure*}

% fig:prec
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-prec}
	\end{center}
	\caption{Winter precipitation rate maps from the five datasets used in this study and summer precipitation map from the WorldClim dataset.}
	\label{fig:prec}
\end{figure*}

% fig:topo
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-topo}
	\end{center}
	\caption{Reference topography used for temperature lapse-rate corrections from the five climate datasets used in the study and ETOPO1 topography used as basal condition for the ice flow model.}
	\label{fig:topo}
\end{figure*}

% fig:cool06
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-cool06}
	\end{center}
	\caption{Ice surface topography (black contours every 1000\,m) and velocity (\unit{m\,yr^{-1}}) after 10\,kyr under a climate 6\degC colder than present for each climate forcing.}
	\label{fig:cool06}
\end{figure*}

% fig:extent
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-extent}
	\end{center}
	\caption{Extent of ice cover after 10\,kyr as a function of applied temperature offsets for each climate forcing.}
	\label{fig:extent}
\end{figure*}

% fig:ivolarea
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=9cm]{cordillera-climate-ivolarea}
	\end{center}
	\julien[inline]{I will make the figure readable in black-and-white and highlight markers corresponding to the ``best'' runs.}
	\caption{Total ice volume and glaciated area after 10\,kyr as a function of temperature offset and climate forcing.}
	\label{fig:ivolarea}
\end{figure}

% fig:best
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-best}
	\end{center}
	\caption{Ice surface topography (black contours every 1000\,m) after 10\,kyr using temperature offsets that lead to similar areas of ice cover for each climate forcing. 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) ice margin (blue line) from \citet{dyke-2004}.}
	\label{fig:best}
\end{figure*}

### 2013-07-01 floats/tables.tex
Physically moved floats to the end

% ----------------------------------------------------------------------
\section{Climate forcing}
\label{sec:climate}
% ----------------------------------------------------------------------

We force PISM with temperature and precipitation data from one observational dataset, three global and one regional reanalyses. Here we present this climate data and describe how we use it as a forcing.

\subsection{Observation data}

WorldClim is a high-resolution climate dataset built from observation data \citep{data:worldclim}. These climate surfaces were generated by spatial interpolation between a large set of weather stations over global land areas, using 30\,arc\,s-aggregated hole-filled SRTM elevation data. This provides a resolution much higher than attained by general circulation models.

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-temp}
	\end{center}
	\caption{Summer temperature maps from the five datasets used in this study and winter temperature map from the WorldClim dataset.}
	\label{fig:temp}
\end{figure*}

Figure~\ref{fig:temp} shows the spatial distribution of summer (JJA) and winter (DJF) air surface temperatures in WorldClim. Temperatures generally decrease from south to north and regions further inland experience colder winters. It should be noted that the temperature gradient is much stronger in the winter than it is in the summer. Temperature reach well above zero during the summer months over the entire modelling domain, except of the highest peaks. In other words, there is a strong contrast in seasonality between coastal and inland regions, even and regions where mean annual temperatures are well below freezing do experience warm summers.

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-prec}
	\end{center}
	\caption{Winter precipitation rate maps from the five datasets used in this study and summer precipitation map from the WorldClim dataset.}
	\label{fig:prec}
\end{figure*}

Figure~\ref{fig:prec} shows the spatial distribution of DJF and JJA precipitation rates in WorldClim. Coastal regions generally receive much more precipitation than inland ones as a result of the continuous orographic barrier formed by the Boundary Ranges, the Coast Mountains and the Cascades. From a glacier mass-balance point of view, this contrast is made even stronger by the difference in timing of the precipitation peak through the year. Although coastal regions experience most precipitation as snow during the accumulation season, inland regions experience dry winters and most of the precipitation falls as rain during the summer months.

In regions like Northern Yukon and Alaska, dry winters and warm summers are unfavourable conditions to ice accumulation and glacial inception despite of the strongly negative present mean annual temperatures. In order to account for these strong gradients in seasonality, we use monthly averages of temperature and precipitation to drive the ice sheet model.

The density of weather stations used by WorldClim in the Northern American Cordillera is highly inhomogeneous. If good coverage exists in the southern parts of our modelling domain, several hundred kilometres can separate neighbouring stations in the north \citep{data:worldclim}. A second drawback of the dataset in the scope of this study is the lack of data across oceans, particularly on the Pacific continental shelf where glaciers have advanced during the last glacial cycle \citep{jackson-clague-1991}.

% ----------------------------------------------------------------------

\subsection{Reanalysis data}

\begin{table*}[t]
	\caption{Characteristic of reanalysis climatologies used to force the ice sheet model.}
	\label{tab:reanalyses}
	\vskip4mm
	\centering
	\begin{tabular}{lllll}
		\tophline
		Reanalysis& Spatial coverage& Averaging period& Resolution& Description\\
		\middlehline
		NCEP/NCAR&  global&     1981 -- 2010& 1.875\degree& \citet{data:ncar}\\
		ERA-Interim&global&     1979 -- 2011& 1.000\degree& \citet{data:erai}\\
		CFSR&       global&     1979 -- 2010& 0.325\degree& \citet{data:cfsr}\\
		NARR&       North America& 1979 -- 2000& 32\,km& \citet{data:narr}\\
		\bottomhline
	\end{tabular}
\end{table*}

Apart from the WorldClim data, we use surface air temperatures and precipitation rates from three global and one regional climate reanalyses to force the ice sheet model: the NCEP/NCAR reanalysis, the ERA-Interim reanalysis, the Climate System Forecast Reanalysis (CFSR) and the North American Regional Reanalysis (NARR). Monthly climatologies from NCEP/NCAR and NARR reanalysis were provided by the NOAA/OAR/ESRL Physical Sciences Division, Boulder, Colorado, USA, from their website at \url{http://www.esrl.noaa.gov/psd/} whereas monthly climatologies from the ERA-Interim and CFSR reanalyses were computed from their monthly mean time series. Further information on the data used is gathered in Table \ref{tab:reanalyses}.

The spatial distribution of JJA air surface temperatures and DJF precipitation rates from the four reanalyses datasets are shown in Figures~\ref{fig:temp} and~\ref{fig:prec}. Summer temperature and winter precipitation are most relevant to the glacier model as they respectively drive summer melt and winter accumulation.

As a mixed product from observations and circulation modelling, we believe that reanalysis may perform best in sparsely monitored regions such as the northernmost American Cordillera.

% ----------------------------------------------------------------------

\subsection{Preprocessing and lapse-rate corrections}

Air surface temperature and precipitation from the WorldClim data, the NCEP/NCAR, ERA-Interim, CFSR and NARR reanalyses were re-projected to Canadian Atlas Lambert conformal conic projection (EPSG code~3978) and bilinearly interpolated to the model resolution of 10\,km. In addition, WorldClim data was extrapolated to oceans using a nearest-neighbour approach. These last two steps are not presented on figures~\ref{fig:temp} and~\ref{fig:prec}.

For the CFSR, an alternative forcing was prepared by smoothing the precipitation field in order to correct for artefacts seen in figure~\ref{fig:prec}. This was done by averaging data locally in a circular neighbourhood of 7\,pixels in diameter prior to re-projection. Yet we will show that this smoothing has very limited effect on the ice sheet model outcome. These preprocessing steps were made in GRASS~GIS.

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-topo}
	\end{center}
	\caption{Reference topography used for temperature lapse-rate corrections from the five climate datasets used in the study and ETOPO1 topography used as basal condition for the ice flow model.}
	\label{fig:topo}
\end{figure*}

Throughout the simulation, the numerical model dynamically applies temperature lapse-rate corrections that account for differences between the climate forcing reference topography and the ice flow model topography on the one hand, and the evolution of ice thickness on the over hand. For reanalysis data, the circulation model surface topography (or surface geopotential height) was used as reference topography. For the WorldClim data, the aggregated hole-filled SRTM altitude field is used as reference topography. As a basal condition for the ice flow model, we use the ETOPO1\citep{data:etopo1} combined topography and bathymetry dataset. The reference topographies from the five forcing datasets, alongside the ETOPO1 data are shown in figure~\ref{fig:topo}. A lapse-rate of 6\unit{\degree C\,km^{-1}} is used in all simulations. No lapse-rate corrections apply to precipitation rates.

>>>>

% floats/tables.tex

% tab:reanalyses
\begin{table*}[t]
	\caption{Characteristic of reanalysis climatologies used to force the ice sheet model.}
	\label{tab:reanalyses}
	\vskip4mm
	\centering
	\begin{tabular}{lllll}
		\tophline
		Reanalysis& Spatial coverage& Averaging period& Resolution& Description\\
		\middlehline
		NCEP/NCAR&  global&     1981 -- 2010& 1.875\degree& \citet{data:ncar}\\
		ERA-Interim&global&     1979 -- 2011& 1.000\degree& \citet{data:erai}\\
		CFSR&       global&     1979 -- 2010& 0.325\degree& \citet{data:cfsr}\\
		NARR&       North America& 1979 -- 2000& 32\,km& \citet{data:narr}\\
		\bottomhline
	\end{tabular}
\end{table*}

### 2013-07-01 sections/climate.tex
Physically moved floats to the end

% ----------------------------------------------------------------------
\section{Climate forcing}
\label{sec:climate}
% ----------------------------------------------------------------------

@@

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-temp}
	\end{center}
	\caption{Summer temperature maps from the five datasets used in this study and winter temperature map from the WorldClim dataset.}
	\label{fig:temp}
\end{figure*}

@@

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-prec}
	\end{center}
	\caption{Winter precipitation rate maps from the five datasets used in this study and summer precipitation map from the WorldClim dataset.}
	\label{fig:prec}
\end{figure*}

@@

\begin{table*}[t]
	\caption{Characteristic of reanalysis climatologies used to force the ice sheet model.}
	\label{tab:reanalyses}
	\vskip4mm
	\centering
	\begin{tabular}{lllll}
		\tophline
		Reanalysis& Spatial coverage& Averaging period& Resolution& Description\\
		\middlehline
		NCEP/NCAR&  global&     1981 -- 2010& 1.875\degree& \citet{data:ncar}\\
		ERA-Interim&global&     1979 -- 2011& 1.000\degree& \citet{data:erai}\\
		CFSR&       global&     1979 -- 2010& 0.325\degree& \citet{data:cfsr}\\
		NARR&       North America& 1979 -- 2000& 32\,km& \citet{data:narr}\\
		\bottomhline
	\end{tabular}
\end{table*}

@@

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-topo}
	\end{center}
	\caption{Reference topography used for temperature lapse-rate corrections from the five climate datasets used in the study and ETOPO1 topography used as basal condition for the ice flow model.}
	\label{fig:topo}
\end{figure*}

>>>>

% sections/climate.tex
% ----------------------------------------------------------------------
\section{Climate forcing}
\label{sec:climate}
% ----------------------------------------------------------------------

@@

@@

@@

@@

### 2013-07-01 sections/concl.tex
Physically moved floats to the end

% section/abstract.tex
% ----------------------------------------------------------------------

\begin{abstract}
\julien[noline]{The abstract is preliminary.}
We present an ensemble of numerical simulations of the former Cordilleran ice sheet forced by present-day climatologies from five different datasets. Surface air temperature and precipitation rates from the NCEP/NCAR reanalysis, the Climate Forecast System Reanalysis, the ERA-Interim reanalysis and the North American Regional Reanalysis are used to force the ice sheet model PISM. Glacial conditions are mimicked by applying constant temperature offsets over the entire modelling domain, and a positive degree-day model is used to compute surface mass balance. The modelled ice sheet appears highly sensitive to the choice of climate forcing. Best results were obtained from the North American Regional Reanalysis, a high-resolution regional reanalysis which assimilates precipitation.
\end{abstract}

>>>>

% section/concl.tex
% ----------------------------------------------------------------------
\conclusions
\label{sec:concl}
% ----------------------------------------------------------------------

\emph{Coming soon...}

### 2013-07-01 sections/intro.tex
Physically moved floats to the end

% ----------------------------------------------------------------------
\introduction
\label{sec:intro}
% ----------------------------------------------------------------------

@@

\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America. The frame delimits this study's modelling domain. The outlines of the former ice sheets depict ice cover at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) after \citet{dyke-2004}. The background map was made with ETOPO1 \citep{data:etopo1} and Natural Earth Data \citep{data:naturalearth}.}
	\label{fig:locmap}
\end{figure}

>>>>

% section/intro.tex
% ----------------------------------------------------------------------
\introduction
\label{sec:intro}
% ----------------------------------------------------------------------

@@

### 2013-07-01 sections/results.tex
Physically moved floats to the end

% ----------------------------------------------------------------------
\section{Results}
\label{sec:results}
% ----------------------------------------------------------------------

@@

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-cool06}
	\end{center}
	\caption{Ice surface topography (black contours every 1000\,m) and velocity (\unit{m\,yr^{-1}}) after 10\,kyr under a climate 6\degC colder than present for each climate forcing.}
	\label{fig:cool06}
\end{figure*}

@@

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-extent}
	\end{center}
	\caption{Extent of ice cover after 10\,kyr as a function of applied temperature offsets for each climate forcing.}
	\label{fig:extent}
\end{figure*}

@@

\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=9cm]{cordillera-climate-ivolarea}
	\end{center}
	\julien[inline]{I will make the figure readable in black-and-white and highlight markers corresponding to the ``best'' runs.}
	\caption{Total ice volume and glaciated area after 10\,kyr as a function of temperature offset and climate forcing.}
	\label{fig:ivolarea}
\end{figure}

@@

\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=13cm]{cordillera-climate-best}
	\end{center}
	\caption{Ice surface topography (black contours every 1000\,m) after 10\,kyr using temperature offsets that lead to similar areas of ice cover for each climate forcing. 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) ice margin (blue line) from \citet{dyke-2004}.}
	\label{fig:best}
\end{figure*}

>>>>

% sections/results.tex
% ----------------------------------------------------------------------
\section{Results}
\label{sec:results}
% ----------------------------------------------------------------------

@@

@@

@@

@@
